Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
chore: remove DQN variations

\subsection{Learning algorithm}
In our experiments, we employed the well-known \emph{Deep Q-Learning} (DQN) algorithm implemented in RLlib.
%
We set the discount factor $\gamma$ to $0.95$, this parameter controls how much future rewards are 
  considered in the decision-making process.
%
A value slightly below $1$ encourages the agent to prioritize immediate rewards while still accounting 
  for long-term benefits, striking a balance between short-term and long-term planning.
%
We chose a learning rate of $0.001$ to control the speed at which the Q-network's weights are updated.
%
This relatively low learning rate ensures stable learning, preventing large updates that could destabilize 
  the training process, specially in complex environments with multiple interacting agents.
%
For the training batch size, we used a value of $32$, which balances computational efficiency and the diversity 
  of experiences in each update. 
%
A smaller batch size could lead to noisier updates, while a larger one might slow down training without
  significantly improving performance.
%
Additionally, we enabled two key features of the DQN algorithm, namely:
  \begin{enumerate*}[label=(\roman*)]
    \item \emph{Double Q-Learning}, to mitigate the overestimation bias that traditional Q-Learning algorithms are prone to. 
      This is particularly important in multi-agent settings, where overestimation can lead to suboptimal policies due to 
      the complex interactions between agents ; and
    \item \emph{Dueling Q-Learning}, which separates the estimation of the state value from the state-dependent action advantages, 
      enabling the agent to better distinguish between the value of being in a given state and the value of choosing 
      specific actions within that state.
  \end{enumerate*}

@@

\begin{figure}
  \centering
  \includegraphics[width=1\linewidth]{figures/behavior.pdf}
  \caption{Wanted and unwanted behaviors.
  On the left, the wanted behavior, the agents correctly cooperate to cover
  two different items.
  While, on the right, the agents do not correctly cooperate covering
  the same item.
  }
  \label{fig:behavior}
\end{figure}

>>>>

\subsection{Learning algorithm}
In our experiments, we employed the well-known \emph{Deep Q-Learning} (DQN) algorithm implemented in RLlib.
%
We set the discount factor $\gamma$ to $0.95$, this parameter controls how much future rewards are 
  considered in the decision-making process.
%
A value slightly below $1$ encourages the agent to prioritize immediate rewards while still accounting 
  for long-term benefits, striking a balance between short-term and long-term planning.
%
We chose a learning rate of $0.001$ to control the speed at which the Q-network's weights are updated.
%
This relatively low learning rate ensures stable learning, preventing large updates that could destabilize 
  the training process, specially in complex environments with multiple interacting agents.
%
For the training batch size, we used a value of $32$, which balances computational efficiency and the diversity 
  of experiences in each update. 
%
A smaller batch size could lead to noisier updates, while a larger one might slow down training without
  significantly improving performance.
%
%Additionally, we enabled two key features of the DQN algorithm, namely:
%  \begin{enumerate*}[label=(\roman*)]
%    \item \emph{Double Q-Learning}, to mitigate the overestimation bias that traditional Q-Learning algorithms are prone to. 
%      This is particularly important in multi-agent settings, where overestimation can lead to suboptimal policies due to 
%      the complex interactions between agents ; and
%    \item \emph{Dueling Q-Learning}, which separates the estimation of the state value from the state-dependent action advantages, 
%      enabling the agent to better distinguish between the value of being in a given state and the value of choosing 
%      specific actions within that state.
%  \end{enumerate*}

@@

\begin{figure}
  \centering
  \includegraphics[width=1\linewidth]{figures/behavior.pdf}
  \caption{Examples of cooperative and uncoordinated behavior. (Left) desired, agents effectively choose different paths to collect different items. (Right) undesired, agents cover the same path to collect the same item.}
  \label{fig:behavior}
\end{figure}
